The shape of dark matter halos in the AURIGA simulations

### 2019-02-19 Paper/paper.tex
edit

In Table \ref{table:shape} we summarize the

@@

\begin{table}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l|ccccc}
 &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
\hline \hline
$\bar{q}$&$0.55^{+0.07}_{-0.07}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$ \\ [0.1cm]
$\bar{s}$&$0.42^{+0.12}_{-0.03}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$\\ [0.1cm]
$\bar{T}$&$0.89^{+0.03}_{-0.08}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$\\ [0.1cm]
\hline
\end{tabular}
\end{center}
\caption{Median values of axial ratios $q,s$ and triaxiality parameter
  $T$ for DM halos in DM-only simulations at different radii. The
  median is computed over the 30 halos in Level 3 simulations.}  
\label{table:median_axial_ratio_DM}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{l|ccccc}
 &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
\hline \hline
$\bar{q}$&$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$\\[0.1cm]
$\bar{s}$&$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$\\[0.1cm] 
$\bar{T}$&$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$\\[0.1cm] 
\hline
\end{tabular}
\end{center}
\caption{
Median values of axial ratios $q,s$ and triaxiality parameter $T$ for
DM halos in MHD simulations at different radii (columns). }  
\label{table:median_axial_ratio_MHD}
\end{table}

>>>>

In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
we summarize the results for the median values of the axis ratio in
the two sets of simulations (DM and MHD). 
The lower/upper bounds correspond to the first/third quartiles. 
The values in Table  \ref{table:median_axial_ratio_DM} shows how halos are
monotonically rounder with increasing radius, while the comparison
against Table \ref{table:median_axial_ratio_MHD} shows that halo are
consistently rounder in MHD simulations at every radius.

@@

\begin{table}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l|ccccc}
 &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
\hline 
$b/a$ &$0.55^{+0.07}_{-0.07}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$ \\ [0.1cm]
$c/a$ &$0.42^{+0.12}_{-0.03}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$\\ [0.1cm]
$T$ &$0.89^{+0.03}_{-0.08}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$\\ [0.1cm]
\end{tabular}
\end{center}
\caption{Median values of axial ratios $q,s$ and triaxiality parameter
  $T$ for DM halos in DM-only simulations at different radii. The
  median is computed over the 30 halos in Level 3 simulations.}  
\label{table:median_axial_ratio_DM}
\end{table}

\begin{table}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l|ccccc}
 &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
\hline 
$b/a$ &$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$\\[0.1cm]
$c/a$ &$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$\\[0.1cm] 
$T$ &$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$\\[0.1cm] 
\end{tabular}
\end{center}
\caption{Median values of axial ratios $q,s$ and triaxiality parameter
  $T$ for DM halos in MHD-only simulations at different radii. The
  median is computed over the 30 halos in Level 3 simulations.}  
\label{table:median_axial_ratio_MHD}
\end{table}
